---
title: "Mass of chaffinches"
author: "Emma Rand"
output:
  bookdown::pdf_document2: default
  bookdown::word_document2: default
  bookdown::html_document2: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      fig.retina = 3)
```


```{r packages}
library(tidyverse)
```

```{r functions}
sum_sq <- function(df, measure, group) {
  df %>% group_by({{ group }}) %>% 
    summarise(ss = sum(({{measure}} - mean({{measure}}))^2))
}

data_summary <- function(df, measure, group) {
  df %>% 
  group_by({{ group }}) %>% 
  summarise(mean = mean({{ measure }}),
            n = length({{ measure }}),
            sd = sd({{ measure }}),
            se = sd/sqrt(n))
}
     
```



# Introduction
The chaffinch, *Fringilla coelebs*, is one of the most widespread and common passerine bird species. It is sexually dimorphic in plumage with males being brightly coloured with a blue-grey cap and rust-red underparts and females being grey-brown with paler underparts. This study aimed to determine whether *F.coelebs* were also sexually dimorphic in size.

# Methods
```{r}
file <- "data-raw/chaff.txt"
chaff <- read_table2(file)
```
We randomly sampled 20 male and 20 female birds on the stray and determined their mass with spring scales.
Analysis was carried out with R version 4.0.2 (R Core Team, 2020) and tidyverse packages (Wickham et al., 2019)

```{r}
chaff <- chaff %>%
  pivot_longer(names_to = "sex", 
               values_to = "mass",
               cols = everything())
```

```{r}
sums_of_sq <- sum_sq(chaff, mass, sex)
```

```{r}
chaff_summary <- data_summary(chaff, mass, sex)
```


# Results
```{r}

```


# Discussion

